Evaluating Open Information Extraction for Ontologization of a Thematic Domain

### 2014-05-08 paper/iswc2014.tex
updates to paper, version sent to Siva for review.

\section{Introduction}
\label{sec:intro}
The advent of the semantic web and the linked open data movements have not only resulted in a growing number of community-built structured data sources, but also catalyzed the development of domain-independent approaches for extracting information from unstructured text, further enriching them. Open information extraction (OIE) is one such paradigm that has emerged in the past decade, and has been used to extract assertions from unstructured data at web-scale with a considerable success [ref]. Until recently, domain-specific approaches to information extraction from text required manual knowledge engineering as a prerequisite [refs]. The OIE approaches, however, do not require a prespecified vocabulary and/or relation-specific input. Therefore, adapting them to information extraction from thematic domains would alleviate the need or manual knowledge engineering.

@@

\section{Open Information Extraction}
\label{sec:oie}
Information extraction is the task of obtaining a set of assertions from the natural language text, featuring the entities and the relations of the corresponding domain. The approaches are diverse ranging from those which learn from the labeled training samples for the desired set of target relations, to those which operate in an unsupervised manner. An easy access to large volume of unstructured text on the web has necessitated approaches that scale appropriately to take advantage of this data. Open information extraction is one such paradigm, which aims to extract the assertions from voluminous data without requiring a pre-specified vocabulary or labeled data for relations [refs].

\subsection{ReVerb \& OpenIE 4.0}
For demonstrating our evaluation framework, we choose two state-of-the-art OIE systems: ReVerb and OpenIE 4.0, which are shown to have outperformed the earlier systems such as TextRunner [ref], $woe^{pos}$ and $woe^{parse}$ [ref]. ReVerb addresses the issue of incoherent and uninformative extractions found with the former approaches, by using few syntactic and lexical constraints [ref]. OLLIE is a successor of ReVerb, and includes the noun-mediated relations which are not handled by the latter. It also incorporates the context of the assertions in the form n-ary relations [ref]. OpenIE 4.0 employs a similar methodology to that of OLLIE, to retrieve assertions by semantic role labeling, also known as shallow semantic parsing.

\subsection{Semantic parsing}
On the other hand, deep semantic parsing is an active research topic in the natural language processing (NLP) community, which aims to obtain a complete logical form of a given sentence. It facilitates applications such as question-answering systems, and further has several direct implications for OIE as it is domain-independent and is shown to be web-scalable [refs]. To our knowledge, there is no existing literature that compares it with the likes of ReVerb and OpenIE 4.0. We therefore built an information extraction wrapper around a state-of-the-art semantic parser, to be compared with the selected OIE approaches. What follows is a brief description of this system.

We use Combinatory Categorial Grammar (CCG, Steedman 2000) as our grammatical framework to parse natural language sentences to logical representation. CCG is known for its transparency between syntax and semantics, i.e. given the syntactic structure (CCG derivation) of a sentence, a semantic (logical) representation can be built deterministically from its derivation. Each word in a sentence is first assigned a CCG category based on its context. Each category represents the syntactic constraints that the word has to satisfy. For example, in Figure.~\ref{fig:ccg_sample}, the word \textit{plays} is assigned a syntactic category $(S\backslash NP)/NP$ implying that \textit{plays} take a noun ($NP$) argument on its right, and a noun argument ($NP$) on its left to form a sentence ($S$). An equivalent semantic category in terms of a lambda function is constructed from the syntactic category, here $\lambda x. \lambda y. \mathrm{plays}(subj,~y) \wedge \mathrm{plays}(obj,~x)$ with \textit{plays} representing the predicate, $x$ and $y$ representing the object (guitar) and subject (John) arguments. CCG defines a set of combinators using which the adjacent categories combine to form syntactic categories of larger text units like phrases (\textit{e.g:} plays guitar), from there on leading to parsing a whole sentence. Correspondingly, the lambda functions of the categories compose, eventually leading to semantic representation of the sentence. The advantage with CCG is that the complexity of obtaining a logical representation of the sentence is simplified into the task of assigning categories to words. We use a modified version of Boxer (Bos et al. 2004) to further convert our sentences of interest to binary assertions of the form <argument 1, relation phrase, argument 2>.
\begin{figure}[!t]
\centering
\includegraphics[width=0.6\linewidth]{figures/ccg_sample.pdf}
\caption{An example showing the sentence `John plays guitar', parsed using CCG.}
\label{fig:ccg_sample}
\end{figure}

\section{Data}
\label{sec:data}
A major challenge in developing technologies for the exploration and the navigation of music repertoires from around the world, lies in obtaining and using their cultural context. The vocabulary used for describing and relating the entities (musical concepts, roles of people involved etc) differs to a great extent from music to music. Most commercial platforms have a limited view of such context, resulting in poor navigation and exploration systems that fail to address the cultural diversity of the world.  Within the music information research community, there is a growing interest for developing culture-aware approaches to address this problem [ref compmusic]. Such approaches are diverse in terms of the data they work with (audio, metadata and contextual-data) and methodologies they employ [ref: mires].

However, to our knowledge, there are no major attempts that use text, arguably the largest openly available data source. As a first step in this direction, we choose to demonstrate our framework in the music domain. Indian art music traditions: Carnatic and Hindustani, have a very distinct character, especially when compared to the popular music styles that drive the music market worldwide [ref]. The terminology and the structuring of the knowledge in these music traditions differs substantially from what people are accustomed to, on most commercial platforms. Therefore, they make a suitable yet challenging thematic domain to analyze the quality of the assertions for ontologization.

Our data consists of the plain text obtained from 618, 697 Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, respectively, after removing the tables, listings, figures, infoboxes and other structured content. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to greatly reduce the number of malformed and highly complex sentences.

We observed that a majority of the sentences featured pronouns. The resulting assertions only partially contribute to ontologization. For instance, consider the sentence `She is a Composer'. The resulting assertion would be <She, is a, Composer>. With a few more of such sentences, it is possible to learn that there exists a semantic category called \textit{composer}. However, such assertions are helpless in identifying objects of the corresponding semantic category. Therefore, the pronouns in the text from each page are resolved using [ref]. There were a few false assertions as a result. However, there is a substantial rise in the recall of the entities in the domain. Table. xx list the total number of sentences, and the number of extractions from each of the OIE systems.
%TODO we can add the number of He/she pronouns resolved to put it in perspective.

@@

\section{Evaluation framework}
\label{sec:framework}
In the information extraction literature, comparing different approaches by their performances on a set of labelled sentences or by employing human judges, is a common practise [refs]. Our goal, however, is to evaluate them by the usefulness of the assertions extracted. We quantify this using a series of tasks that help in understanding the coverage of the entities and the relations of a given domain in the extracted assertions, quantitatively and qualitatively.  The tasks discussed in the first part of the evaluation comparing the volume of the assertions. while in the second part, we validate to what extent the assertions yield to be structured. We then juxtapose and compare the results from both parts of the evaluation.

@@

\subsection{Qualitative assessment}
The tasks discussed in this section are complementary to those presented in the former, validating whether the quantitative observations correlate with the performances of OIE approaches on various tasks in ontologization. For this, we consider the three fundamental tasks of ontologization: object identification, concept identification and semantic relation extraction [refs].

\subsubsection{Concept identification.} It is the task of identifying the semantic categories in the domain. The second argument from all the assertions featuring the subsumption relation type are collected. They are disambiguated based on their spellings, mostly automatically using string matching algorithms with minimal manual intervention where necessary. The resulting arguments are taken to be concepts in the taxonomy of the given domain. We compare the coverage of this set of concepts against the ontologies manually built for each of the Carnatic and Hindustani music.

\subsubsection{Object identification.} It concerns with finding the entities of the given domain and assigning a semantic category to them. The set of first arguments from all the assertions are considered as candidates for being objects in the domain. A list of titles of the Wikpedia pages in the domain along with the categories each page belong to, is acquired.  The page titles correspond to objects, and the categories are manually mapped to concepts in our ontology. This constitutes the reference with which we compare the coverage of objects identified using the assertions from each of the OIE approaches.

For evaluating the first part of object identification, i.e., finding the entities of the given domain, we measure the overlap between the candidate objects from each approach with the reference set. The second part, semantic category assignment, is evaluated using two methods. In the first method, we manually build a set of rules using subsumption relation type for each semantic category. The objects satisfying the rules for a given semantic category are assigned to it. The second method takes advantage of the full spectrum of relation-types extracted. Each semantic category is bootstrapped using a seedset of objects belonging to it.

%TODO: write about the bootstrapping approach.

\subsubsection{Semantic relation extraction.} It refers to the relation types other than those which convey concept hierarchies. The relation shown in Figure. xx is one such example, where the relation \textit{plays} connects \textit{person} and \textit{musical instrument} semantic categories. We formulate two measures  to compare the OIE approaches in this task: \textit{breadth} and \textit{depth} of relation types. \textit{Breadth} corresponds to the number of valid relation types identified for each semantic category, and the \textit{depth} corresponds to the number of valid assertions for a given relation type.

\section{Results and discussion}
\subsection{Quantitative assessment}
\begin{figure}
\label{fig:quant-sentences}
\begin{center}
        \subfigure[][Carnatic music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-sentence.pdf}
		 \label{fig:quant-sentences-carnatic}
        }% 
        \qquad
        \subfigure[][Hindustani music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-sentence.pdf}
		 \label{fig:quant-sentences-hindustani}
        }%
\end{center}
\caption{Distribution of number of extracted assertions using each of the approaches, per sentence.}
\end{figure}

\begin{figure}
\label{fig:quant-object}
\begin{center}
        \subfigure[][Carnatic music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-argument.pdf}
		 \label{fig:quant-object-carnatic}
        }% 
        \qquad
        \subfigure[][Hindustani music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-argument.pdf}
		 \label{fig:quant-object-hindustani}
        }%
\end{center}
\caption{Distribution of number of extracted assertions using each of the approaches, per object.}
\end{figure}

\begin{figure}
\label{fig:quant-reltype}
\begin{center}
        \subfigure[][Carnatic music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-reltype.pdf}
		 \label{fig:quant-reltype-carnatic}
        }% 
        \qquad
        \subfigure[][Hindustani music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-reltype.pdf}
		 \label{fig:quant-reltype-hindustani}
        }%
\end{center}
\caption{Distribution of number of extracted assertions using each of the approaches, per relation type.}
\end{figure}

\begin{figure}
\label{fig:quant-concept}
\begin{center}
        \subfigure[][Carnatic music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-class.pdf}
		 \label{fig:quant-concept-carnatic}
        }% 
        \qquad
        \subfigure[][Hindustani music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-class.pdf}
		 \label{fig:quant-concept-hindustani}
        }%
\end{center}
\caption{Distribution of number of extracted assertions using each of the approaches, per concept.}
\end{figure}

\subsection{Qualitative assessment}
\subsubsection{Object identification.}
\begin{figure}
\label{fig:qual-object-rulebased}
\begin{center}
        \subfigure[][Carnatic music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/rule-based/carnatic_music/class-agreement-with-wikipedia.pdf}
		 \label{fig:qual-object-rulebased-carnatic}
        }% 
        \qquad
        \subfigure[][Hindustani music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/rule-based/hindustani_music/class-agreement-with-wikipedia.pdf}
		 \label{fig:qual-object-rulebased-hindustani}
        }%
\end{center}
\caption{Results for rule-based semantic category assignment to objects identified in the domain.}
\end{figure}

\begin{figure}
\label{fig:qual-object-rulebased-inter}
\begin{center}
        \subfigure[][Carnatic music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/rule-based/carnatic_music/class-agreement-inter-method.pdf}
		 \label{fig:qual-object-rulebased-inter-carnatic}
        }% 
        \qquad
        \subfigure[][Hindustani music]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/rule-based/hindustani_music/class-agreement-inter-method.pdf}
		 \label{fig:qual-object-rulebased-inter-hindustani}
        }%
\end{center}
\caption{Inter-approach agreement for semantic category assignment of the objects that correspond to false positives by our reference data.}
\end{figure}

\begin{figure}
\label{fig:qual-object-bootstrapping-carnatic}
\begin{center}
        \subfigure[][Musicians]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/carnatic_music/carnatic_musicians.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-musicians}
        }% 
        \qquad
        \subfigure[][Composers]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/carnatic_music/carnatic_composers.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-composers}
        }%
        \\
        \subfigure[][Instrumentalists]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/carnatic_music/carnatic_instrumentalists.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-instrumentalists}
        }% 
        \qquad
        \subfigure[][Singers]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/carnatic_music/carnatic_singers.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-singers}
        }%
        \\
        \subfigure[][Ragas]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/carnatic_music/carnatic_ragas.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-ragas}
        }% 
        \qquad
        \subfigure[][Compositions]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/carnatic_music/carnatic_compositions.pdf}
		 \label{fig:qual-object-bootstrapping-carnatic-compositions}
        }%
\end{center}
\caption{Carnatic Results.}
\end{figure}

\begin{figure}
\label{fig:qual-object-bootstrapping-hindustani}
\begin{center}
        \subfigure[][Musicians]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/hindustani_music/hindustani_musicians.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-musicians}
        }% 
        \qquad
        \subfigure[][Composers]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/hindustani_music/hindustani_composers.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-composers}
        }%
        \\
        \subfigure[][Instrumentalists]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/hindustani_music/hindustani_instrumentalists.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-instrumentalists}
        }% 
        \qquad
        \subfigure[][Singers]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/hindustani_music/hindustani_singers.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-singers}
        }%
        \\
        \subfigure[][Ragas]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/bootstrapping/hindustani_music/hindustani_ragas.pdf}
		 \label{fig:qual-object-bootstrapping-hindustani-ragas}
        }% 
\end{center}
\caption{Hindustani Results.}
\end{figure}

\subsubsection{Concept identification.}
\subsubsection{Semantic relation extraction.}

>>>>

\section{Introduction}
\label{sec:intro}
The advent of the semantic web and the linked open data movements have not only resulted in a growing number of community-built structured data sources, but also catalyzed the development of domain-independent approaches for extracting information from unstructured text, further enriching them. Open information extraction (OIE) is one such paradigm that has emerged in the past decade, and has been used to extract assertions from unstructured data at web-scale with a considerable success~\cite{Etzioni2008a}. Until recently, domain-specific approaches to information extraction from text required manual knowledge engineering as a prerequisite~\cite{Sarawagi2008}. The OIE approaches, however, do not require a prespecified vocabulary and/or relation-specific input. Therefore, adapting them to information extraction from thematic domains would alleviate the need or manual knowledge engineering.

@@

\section{Open Information Extraction}
\label{sec:oie}
Information extraction is the task of obtaining a set of assertions from the natural language text, featuring the entities and the relations of the corresponding domain. The approaches are diverse ranging from those which learn from the labeled training samples for the desired set of target relations, to those which operate in an unsupervised manner. An easy access to large volume of unstructured text on the web has necessitated approaches that scale appropriately to take advantage of this data. Open information extraction aims to extract the assertions from voluminous data without requiring a pre-specified vocabulary or labeled data for relations~\cite{Etzioni2008a}.

\subsection{ReVerb \& OpenIE 4.0}
For demonstrating our evaluation framework, we choose two state-of-the-art OIE systems: ReVerb~\cite{Fader2011a} and OpenIE 4.0~\cite{Mausam2012a}, which are shown to have outperformed the earlier systems such as TextRunner~\cite{Etzioni2008a}, $woe^{pos}$ and $woe^{parse}$~\cite{Wu2010a}. ReVerb addresses the issue of incoherent and uninformative extractions found with the former approaches, by using few syntactic and lexical constraints. OLLIE is a successor of ReVerb, and includes the noun-mediated relations which are not handled by the latter. It also incorporates the context of the assertions in the form n-ary relations. OpenIE 4.0 employs a similar methodology to that of OLLIE, to retrieve assertions by semantic role labeling, also known as shallow semantic parsing. The implementations for both ReVerb and OpenIE 4.0 are available online\footnote{Available at https://github.com/knowitall/}.

\subsection{Semantic parsing}
On the other hand, deep semantic parsing is an active research topic in the natural language processing (NLP) community, which aims to obtain a complete logical form of a given sentence. It facilitates applications such as question-answering systems, and further has several direct implications for OIE as it is domain-independent and is shown to be web-scalable~\cite{Harrington2007}. To our knowledge, there is no existing literature that compares it with the likes of ReVerb and OpenIE 4.0. We therefore built an information extraction wrapper around a state-of-the-art semantic parser, to be compared with the selected OIE approaches. What follows is a brief description of this system.

We use Combinatory Categorial Grammar (CCG)~\cite{Steedman:2000:SP:332037} as our grammatical framework to parse natural language sentences to logical representation. CCG is known for its transparency between syntax and semantics, i.e. given the syntactic structure (CCG derivation) of a sentence, a semantic representation can be built deterministically from its derivation. Each word in a sentence is first assigned a CCG category based on its context. Each category represents the syntactic constraints that the word has to satisfy. For example, in Figure.~\ref{fig:ccg_sample}, the word \textit{plays} is assigned a syntactic category $(S\backslash NP)/NP$ implying that \textit{plays} take a noun ($NP$) argument on its right, and a noun argument ($NP$) on its left to form a sentence ($S$). An equivalent semantic category in terms of a lambda function is constructed from the syntactic category, here $\lambda x. \lambda y. \mathrm{plays}(subj,~y) \wedge \mathrm{plays}(obj,~x)$ with \textit{plays} representing the predicate, $x$ and $y$ representing the object (guitar) and subject (John) arguments. CCG defines a set of combinators using which the adjacent categories combine to form syntactic categories of larger text units like phrases (\textit{e.g:} plays guitar), from there on leading to parsing a whole sentence. Correspondingly, the lambda functions of the categories compose, eventually leading to semantic representation of the sentence. The advantage with CCG is that the complexity of obtaining a logical representation of the sentence is simplified into the task of assigning categories to words. We use a modified version of Boxer~\cite{Bos2004} to further convert our sentences of interest to binary assertions of the form <argument 1, relation phrase, argument 2>.
\begin{figure}[!t]
\centering
\includegraphics[width=0.6\linewidth]{figures/ccg_sample.pdf}
\caption{An example showing the sentence `John plays guitar', parsed using CCG.}
\label{fig:ccg_sample}
\end{figure}

\section{Data}
\label{sec:data}
A major challenge in developing technologies for the exploration and the navigation of music repertoires from around the world, lies in obtaining and using their cultural context. The vocabulary used for describing and relating the entities (musical concepts, roles of people involved etc) differs to a great extent from music to music. Most commercial platforms have a limited view of such context, resulting in poor navigation and exploration systems that fail to address the cultural diversity of the world.  Within the music information research community, there is a growing interest for developing culture-aware approaches to address this problem~\cite{Serra2011}. Such approaches are diverse in terms of the data they work with (audio, metadata and contextual-data) and methodologies they employ~\cite{Serra2013a}.

However, to our knowledge, there are no major attempts that use text, arguably the largest openly available data source. As a first step in this direction, we choose to demonstrate our framework in the music domain. Indian art music traditions: Carnatic and Hindustani, have a very distinct character, especially when compared to the popular music styles that drive the music market worldwide. The terminology and the structuring of the knowledge in these music traditions differs substantially from what people are accustomed to, on most commercial platforms~\cite{Krishna2012}. Therefore, they make a suitable yet challenging thematic domain to analyze the quality of the assertions for ontologization.

Our data consists of the plain text obtained from the Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, after removing the tables, listings, figures, infoboxes and other structured content. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to greatly reduce the number of malformed and highly complex sentences.

We observed that a majority of the sentences featured pronouns. The resulting assertions only partially contribute to ontologization. For instance, consider the sentence `She is a Composer'. The resulting assertion would be <She, is a, Composer>. With a few more of such sentences, it is possible to learn that there exists a semantic category called \textit{composer}. However, such assertions are helpless in identifying objects of the corresponding semantic category. Therefore, the pronouns in the text from each page are resolved using the deterministic coreference resolution described in~\cite{Lee2013b}\footnote{Available online at http://nlp.stanford.edu/software/dcoref.shtml}. There were a few false assertions as a result. However, there is a substantial rise in the recall of the entities in the domain. Table.~\ref{tab:data} list the total number of sentences, and the number of extractions from each of the OIE systems. ReVerb and Open IE 4.0 associate a confidence score with the extracted assertions. We did not however choose to filter these based on this score, as \cite{Soderland2010} have found that a system with a better recall at the cost of lower precision is actually preferred for knowledge-base population using open information extraction. We ignore the context from the n-ary assertions to convert them to binary form.

%TODO we can add the number of He/she pronouns resolved to put it in perspective.

@@

\section{Evaluation framework}
\label{sec:framework}
In the information extraction literature, comparing different approaches by their performances on a set of labelled sentences or by employing human judges, is a common practice~\cite{Fader2011a,Mausam2012a}. Our goal, however, is to evaluate them by the usefulness of the assertions extracted. We quantify this using a series of tasks that help in understanding the coverage of the entities and the relations of a given domain in the extracted assertions, quantitatively and qualitatively.  The tasks discussed in the first part of the evaluation comparing the volume of the assertions. while in the second part, we validate to what extent the assertions yield to be structured. We then juxtapose and compare the results from both parts of the evaluation.

@@

\subsection{Qualitative assessment}
The tasks discussed in this section are complementary to those presented in the former, validating whether the quantitative observations correlate with the performances of OIE approaches on various tasks in ontologization. For this, we consider the three fundamental tasks of ontologization: object identification, concept identification and semantic relation extraction~\cite{Petasis2011}.

\subsubsection{Concept identification.} It is the task of identifying the semantic categories in the domain. The second argument from all the assertions featuring the subsumption relation type are collected. They are disambiguated based on their spellings, mostly automatically using string matching and edit distance measures\footnote{Available at https://github.com/gopalkoduri/string-matching} with minimal manual intervention where necessary. The resulting arguments are taken to be the candidate concepts of the given domain. We compare the coverage of these against the classes in the ontologies manually engineered with the help of music experts, for each of the Carnatic and Hindustani music\footnote{Available at https://github.com/gopalkoduri/ontologies}.

\subsubsection{Object identification.} It concerns with finding the entities of a given domain and assigning a semantic category to them. The set of first arguments from all the assertions are considered as candidates for being objects in the domain. A list of titles of the Wikpedia pages in the domain along with the categories each page belong to, is acquired. The page titles correspond to objects, and the categories are manually mapped to classes in our ontology. This constitutes the reference with which we compare the results from the two subtasks of object identification.

For evaluating the first subtask of object identification, i.e., finding the entities of the given domain, we measure the overlapping ($O$) and the residual ($R$) portions of the candidate objects from each approach with respect to the reference set. If $X$ is the set of candidate objects and $Y$ is the reference set, $O$ and $R$ are defined as:
\begin{eqnarray}
\label{eq:overlap}
O(X, Y) = \frac{\left|X \cap Y \right|}{\left|Y\right|} \\\nonumber
R(X, Y) = \frac{\left|X - Y \right|}{\left|X\right|}
\end{eqnarray}

The second part, semantic category assignment, is evaluated using two methods. In the first method, we manually build a set of rules over subsumption relation type for each semantic category. For instance, for an object to belong to the semantic category \textit{singers}, it must have either of the words \textit{vocalist} or \textit{singer} in the second argument of the corresponding assertions with subsumption relation type. All the objects satisfying the rules for a given semantic category are assigned to it.
%TODO include the rules?

In the second method, a given object is reduced to be represented by a term vector corresponding to the words from second arguments of the assertions it is part of. Following this, each semantic category is initiated with a seedset of objects belonging to it. A given semantic category is taken to be an abstract super object, represented by the union of the term vectors of the constituting objects. A bootstrapping mechanism is started, which in a given iteration, finds the closest object to the given semantic category and adds it to the seedset, and recomputes its representation. The distance between given two objects corresponds to the cosine similarity between the term vectors transformed using TF-IDF, followed by Latent Semantic Indexing~\cite{rehurek_lrec}. Unlike the first approach, which is constrained to assertions with subsumption relation type, this method takes advantage of the full spectrum of relation types. Results from the both methods are evaluated using $O$ and $R$ measures from eq.~\ref{eq:overlap}, where $X$ and $Y$ correspond to the candidate set of objects obtained using one of the methods for a given semantic category, and the reference set of objects respectively.

\subsubsection{Semantic relation extraction.} It refers to the relation types other than those which convey concept hierarchies. The assertion shown in Figure. xx is one such example, where \textit{plays} is a relation that connects \textit{person} and \textit{musical instrument} semantic categories. We formulate two measures  to compare the OIE approaches in this task: breadth ($B$) and depth ($D$) of the identified relation types. $B$ corresponds to the absolute number of valid relation types identified for each semantic category, and the $D$ corresponds to the number of valid assertions for a given relation type. This is mostly done manually.
\begin{figure}[!b]
\label{fig:quant-carnatic}
\begin{center}
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-sentence.pdf}
		 \label{fig:quant-carnatic-sentences}
        }% 
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-argument.pdf}
		 \label{fig:quant-carnatic-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-reltype.pdf}
		 \label{fig:quant-carnatic-reltype}
        }% 
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/carnatic_music/extrations-per-class.pdf}
		 \label{fig:quant-carnatic-concept}
        }% 
\end{center}
\caption{Distribution of number of extracted assertions from each of the approaches for Carnatic music, across different aspects.}
\end{figure}

\section{Results and discussion}
\subsection{Quantitative assessment}
Figs.~\ref{fig:quant-carnatic-sentences} and \ref{fig:quant-hindustani-sentences} show the distribution of the number of extracted assertions using each of the OIE approaches, across sentences in Carnatic and Hindustani music, respectively. Notice that the y-axis is a log scale. Between ReVerb and OpenIE 4.0, the latter seem to perform better, which can be attributed to the noun mediated relations. The semantic parsing based system, however, retrieves substantially more relations per sentence than these two. A tight coupling between syntax and semantics proves to be advantageous in chunking different types of assertions, as well as relating entities far off each other in a given sentence. For instance, in sentences which feature a single subject, but multiple relations (e.g: x is a y, born in z to a and b.), it performed thoroughly well compared to others. The difference between their performances for Carnatic and Hindustani music is negligible, which shows that this result is consistent.
\begin{figure}[!t]
\label{fig:quant-hindustani}
\begin{center} 
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-sentence.pdf}
		 \label{fig:quant-hindustani-sentences}
        }%
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-argument.pdf}
		 \label{fig:quant-hindustani-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-reltype.pdf}
		 \label{fig:quant-hindustani-reltype}
		}%
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/quantitative/hindustani_music/extrations-per-class.pdf}
		 \label{fig:quant-hindustani-concept}
        }%
\end{center}
\caption{Distribution of number of extracted assertions from each of the approaches for Hindustani music, across different aspects.}
\end{figure}

Figs.~\ref{fig:quant-carnatic-object} and \ref{fig:quant-hindustani-object} show the corresponding distribution across objects. Recall that we defined an object to be the first argument of an assertion. The few objects with a disproportionately high number of extractions are usually the pronouns (despite resolving most of them), followed by musical terms. The semantic parsing based system retrieves slightly more number of assertions per object compared to OpenIE 4.0, which in turn performs better than ReVerb. We observed some redundancy in assertions for a given object, which is beneficial as this can be used as a measure of confidence in asserting the corresponding relation. In order to analyze this, we have also plotted the distributions with unique extractions across objects (shown in dashed lines in the figures). For Carnatic music, we can observe that the semantic parsing based system retrieves substantially more number of redundant assertions per object compared to the other two. This difference, however, is less obvious in the case Hindustani music.

Figs.~\ref{fig:quant-carnatic-reltype} and \ref{fig:quant-hindustani-reltype} show the distribution of the number of extracted assertions across the relation types. The results for semantic parsing based system and OpenIE 4.0 are more or less the same, both of which are substantially better than ReVerb. The redundancy in assertions, seen as the difference between the distributions shown by solid and dashed lines, is not as pronounced as it is for objects. The decline in the total number of relation-types as the number of extractions go higher, is less steep than in the case of objects. Unless the vocabulary in the domain is itself limited, this may indicate a slightly better coverage of relation types compared to that of the objects in the domain.

Figs.~\ref{fig:quant-carnatic-concept} and \ref{fig:quant-hindustani-concept} show the distribution of the number of extracted assertions across the concepts. Recall that a concept is defined to be the second argument of an assertion. The difference between the semantic parsing based system and the other two is quite marked, both for Carnatic and Hindustani music, with the former retrieving more assertions per concept. For Hindustani music, the coverage of concepts in the assertions of ReVerb and OpenIE 4.0 is very low, with no concept having more than 20 assertions.

To summarize, the results indicate that the semantic parsing based system has a better coverage of objects, concepts and relation types of the domain than OpenIE 4.0, which is followed by ReVerb. It also retrieves more assertions per sentence compared to the other two. Note that this section has only provided the quantitative information, which by no means is complete in itself. The results we discuss in the following section complement these providing qualitative observations along the same dimensions (i.e., objects, concepts and relation types).

\subsection{Qualitative assessment}
In this section, we present the results for various tasks in the ontologization of Indian art music domain: concept identification, object identification and semantic relation extraction.
\subsubsection{Concept identification.}
Recall that we define candidate concepts to be the collection of second arguments from the assertions of a given OIE system. We filter out those candidates which appear less than 5 times. We map the rest to the classes in the ontologies as described in sec.~\ref{sec:framework}. Table.~\ref{tab:concept_identification} shows the number of classes in the ontolgies for each music, and the number of concepts mapped from the assertions of the OIE systems.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Ontology} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 53 & 4 & 4 & 22 \\
  Hindustani  & 55 & 1 & 2 & 9 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of classes in the ontologies for each music, and the number of concepts mapped from the assertions of the OIE systems.}
\label{tab:concept_identification}
\end{table}

\subsubsection{Object identification.}
The first subtask in this part is to find the entities in the domain. The candidate entities from each OIE system are defined to be the collection of first arguments from all its assertions. Table.~\ref{tab:object_identification} shows the total number of entities in the reference data taken from Wikipedia for each music, and the number of entities in the intersection of these with the candidate entities of each OIE system. There is no marked difference between the results, with nearly all the systems having about 60\% of the entities from reference data in their assertions. Further, these correspond to only about 7\% of all the candidate entities.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Reference} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 618 & 349 & 364 & 364 \\
  Hindustani  & 697 & 396 & 410 & 399 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of entities in the reference data for each music, and those identified using the OIE systems.}
\label{tab:object_identification}
\end{table}

\begin{figure}[!t]
\label{fig:qual-object-rulebased}
\begin{center}
        \subfigure[][Overlap with reference data.]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/rule-based/carnatic_music/class-agreement-with-wikipedia.pdf}
		 \label{fig:qual-object-rulebased-carnatic-wikipedia}
        }% 
        \qquad
        \subfigure[][Inter-system agreement for residual object cadidates.]{%
		 \includegraphics[width=0.45\linewidth]{../data/results/qualitative/object-identification/rule-based/carnatic_music/class-agreement-inter-method.pdf}
		 \label{fig:qual-object-rulebased-carnatic-inter}
